data_collation

### 2024-05-17 scripts/data_collation.Rmd
added updated swath data

@@

>>>>

# rename moprph category columns in morph and kelp data
morph_data <- morph_data %>%
  rename(
    "BLADE_WIDTH_CM" = "WIDTH_CM")

kelp_data <- kelp_data %>%
  rename(
    "BLADE_WIDTH_CM" = "WIDTH_CM",
    "BLADE_LENGTH_CM" = "LENGTH_CM")

#MAKE STIPE LENGTH NUMERICAL INSTEAD OF CHARACTER in morph data
morph_data$STIPE_LENGTH_CM <- as.numeric(morph_data$STIPE_LENGTH_CM)

#combine kelp and morph daat
morph_data <- left_join(morph_data, kelp_data)

@@

# output updated dataframe
write.csv(swath_data, "output/cleaned_data/swath.data.clean.csv", row.names = FALSE)
